---
title: "jsonmatch"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA)
```

[![Travis-CI Build Status](https://travis-ci.org/chiefBiiko/jsonmatch.svg?branch=master)](https://travis-ci.org/chiefBiiko/jsonmatch) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/chiefBiiko/jsonmatch?branch=master&svg=true)](https://ci.appveyor.com/project/chiefBiiko/jsonmatch) [![Coverage Status](https://codecov.io/gh/chiefBiiko/jsonmatch/branch/master/graph/badge.svg)](https://codecov.io/gh/chiefBiiko/jsonmatch)

***

Simple `JSON` matching.

***

## Get it

```{r, eval=FALSE}
devtools::install_github('chiefBiiko/jsonmatch')
```

***

## Usage

`jsonmatch::jsonmatch(json, pattern, auto_unbox=FALSE, strict=TRUE)`

+ `json` Character. In-memory `JSON` string or filename. **required**
+ `pattern` Character. Subset pattern. **required**
+ `auto_unbox` Logical. Unbox `JSON`? Default: `FALSE`. **optional**
+ `strict` Logical. Only allow valid `JSON`? Default: `TRUE`. **optional**

`pattern` allows matching keys of `JSON` arrays and objects. Its syntax rules are as follows:

+ Array values are referenced via their index (zero-based): 
`[0]` or `[2:]` or `[2:3]`
+ Object values are referenced via their key: 
`.key` or `.k*y` or `.*y` or `.k*` or `.*`
+ Multiple *subset paths* are separated by a comma: `.keyA[0],.keyB[0]`

For the rationale of `auto_unbox` check out [`boxjson`](https://github.com/chiefBiiko/boxjson). If `strict` is `TRUE` and `jsonlite::validate(json)` evaluates to `FALSE` an error is thrown.

```{r}
# some JSON
some.json <- jsonlite::toJSON(list(list(name='herman', gang='almans'), 
                                   list(name='habibo', gang=c('haji', '419'))))

# peek at it
cat('some JSON:\n', some.json, sep='')
```

```{r}
# who u with
gangs <- jsonmatch::jsonmatch(some.json, '[0:].gang')
cat('gangs:\n', gangs, sep='')
```

***

## License

MIT
